How topos theory can help commutative algebra

### 2018-07-09 slides-como2018.tex
typo

  Beautiful constructive proofs can also be found in Richman's note on
  \fixedhref{https://www.ams.org/journals/proc/1988-103-04/S0002-9939-1988-0954974-5/S0002-9939-1988-0954974-5.pdf}{nontrivial
  uses of nontrivial rings} and in the
  \fixedhref{https://arxiv.org/abs/1605.04832}{recent textbook by Lombardi and
  Quitté} on constructive commutative algebra.}

@@

  \small\centering
  \scalebox{0.83}{\begin{tabular}{ll}
    \toprule
    externally & internally to $\Sh(X)$ \\
    \midrule
    sheaf of sets & set \\
    %sheaf of rings & ring \\
    sheaf of modules & module \\
    sheaf of finite type & finitely generated module \\
    % finite locally free sheaf & finite free module \\
    % coherent sheaf & coherent module \\
    tensor product of sheaves & tensor product of modules \\
    % sheaf of Kähler differentials & module of Kähler differentials \\
    sheaf of rational functions & total quotient ring of~$\O_X$ \\
    dimension of $X$ & Krull dimension of~$\O_X$ \\
    spectrum of a sheaf of~$\O_X$-algebras & ordinary spectrum [with a twist] \\
    big Zariski topos of $X$ & big Zariski topos of the ring $\O_X$ [with a twist] \\
    higher direct images & sheaf cohomology \\
    \bottomrule
  \end{tabular}}

>>>>

  Beautiful constructive proofs can also be found in Richman's note on
  \fixedhref{https://www.ams.org/journals/proc/1988-103-04/S0002-9939-1988-0954974-5/S0002-9939-1988-0954974-5.pdf}{nontrivial
  uses of trivial rings} and in the
  \fixedhref{https://arxiv.org/abs/1605.04832}{recent textbook by Lombardi and
  Quitté} on constructive commutative algebra.}

@@

  \small\centering
  \scalebox{0.83}{\begin{tabular}{ll}
    \toprule
    externally & internally to $\Sh(X)$ \\
    \midrule
    sheaf of sets & set \\
    % sheaf of rings & ring \\
    sheaf of modules & module \\
    sheaf of finite type & finitely generated module \\
    % finite locally free sheaf & finite free module \\
    % coherent sheaf & coherent module \\
    tensor product of sheaves & tensor product of modules \\
    % sheaf of Kähler differentials & module of Kähler differentials \\
    sheaf of rational functions & total quotient ring of~$\O_X$ \\
    dimension of $X$ & Krull dimension of~$\O_X$ \\
    spectrum of a sheaf of~$\O_X$-algebras & ordinary spectrum [with a twist] \\
    big Zariski topos of $X$ & big Zariski topos of the ring $\O_X$ [with a twist] \\
    higher direct image & sheaf cohomology \\
    \bottomrule
  \end{tabular}}
